---
title: "Leah Script"
output: html_document
date: "`r Sys.Date()`"
---

## Turn on our Packages

Note, if you turn on `tidyverse` package there is no need to load dplyr, ggplot, or stringer etc. I also change the packages that I used based on the following [tutorial](https://quantdev.ssri.psu.edu/sites/qdev/files/GCM_Chp3_Tutorial_2.html) and [here](https://ourcodingclub.github.io/tutorials/mixed-models/#what).

```{r}
library(reshape)
library(tidyverse)
library(kableExtra)
library(matrixStats)
library(lme4)
library(nlme)
library(broom.mixed)
library(purrr)
```

# Read in Our Data

Note: I prefer working with data in open format, so I converted to csv format

```{r}
comb2 <- read_csv("../nihl-r-classes-data-raw/comb2_sub.csv")
```

# Coercied the variables as numbers

```{r}
comb2_sub <- read_csv("../nihl-r-classes-data-raw/comb2_sub.csv", 
    col_types = cols(X.x = col_number(), 
        tfmri_sst_all_beh_correct.stop_numtrials = col_number(), 
        tfmri_sst_all_beh_correct.stop_rate = col_number(), 
        discrimination_matrix_q5 = col_number(), 
        discrimination_matrix_q6 = col_number(), 
        discrimination_matrix_q7 = col_number(),  
tfmri_nback_all_emotion.vs.neutface_beta_cort.destrieux_g.temporal.middle.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.destrieux_g.temporal.middle.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.opercular.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.orbital.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.triangul.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.sup.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.Pre.SMA.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.opercular.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.orbital.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.triangul.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.sup.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.Pre.SMA.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.opercular.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.orbital.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.triangul.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.sup.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.pariet.inf.supramar.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.opercular.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.orbital.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.inf.triangul.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.front.sup.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.destrieux_g.pariet.inf.supramar.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.destrieux_g.temporal.middle.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.destrieux_g.temporal.middle.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_caudate.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_putamen.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_caudate.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_putamen.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_caudalanteriorcingulate.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_inferiorparietal.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_lateraloccipital.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsopercularis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsorbitalis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parstriangularis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_caudalanteriorcingulate.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_inferiorparietal.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_lateraloccipital.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsopercularis.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsorbitalis.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parstriangularis.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_subcort.aseg_caudate.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_subcort.aseg_putamen.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_subcort.aseg_caudate.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_subcort.aseg_putamen.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_caudalanteriorcingulate.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_inferiorparietal.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_lateraloccipital.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parsopercularis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parsorbitalis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parstriangularis.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_caudalanteriorcingulate.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_inferiorparietal.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_lateraloccipital.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parsopercularis.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parsorbitalis.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_sem_cort.desikan_parstriangularis.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_putamen.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_amygdala.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_accumbens.area.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_putamen.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_amygdala.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_subcort.aseg_accumbens.area.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_caudalmiddlefrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_lateralorbitofrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_medialorbitofrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_parsopercularis.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_parstriangularis.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_rostralanteriorcingulate.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_rostralmiddlefrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_caudalmiddlefrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_lateralorbitofrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_medialorbitofrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_parsopercularis.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_parstriangularis.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_rostralanteriorcingulate.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_rostralmiddlefrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_putamen.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_amygdala.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_accumbens.area.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_putamen.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_amygdala.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_subcort.aseg_accumbens.area.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_caudalmiddlefrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_lateralorbitofrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_medialorbitofrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_parsopercularis.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_parstriangularis.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_rostralanteriorcingulate.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_rostralmiddlefrontal.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_caudalmiddlefrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_lateralorbitofrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_medialorbitofrontal.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_parsopercularis.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_parstriangularis.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_rostralanteriorcingulate.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_sem_cort.desikan_rostralmiddlefrontal.rh= col_number(),
age= col_number(),
reshist_state_racism_factor.y= col_number(),
Mean_Discrimination= col_number(),
SD_Discrimination= col_number(),
Z_Score= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_vlPFC.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_vlPFC.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_vmPFC.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_vmPFC.lh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_dlPFC.rh= col_number(),
tfmri_nback_all_emotion.vs.neutface_beta_cort.desikan_dlPFC.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_vlPFC.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_vlPFC.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.front.gyrus.rh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.front.gyrus.lh= col_number(),
X.y= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.pariet.inf.supramar.lh= col_number(),
tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.pariet.inf.supramar.rh= col_number(),
X= col_number(),
tfmri_sst_all_beh_total_mssrt= col_number(),
mri_info_device.serial.number= col_number(),
        tfmri_sst_all_beh_total_mssrt = col_number()))
```

## Convert variables to factors

```{r}
comb2_sub$race.4level <- as.factor(comb2_sub$race.4level)
comb2_sub$sex_at_birth <- as.factor(comb2_sub$sex_at_birth)

class(comb2_sub$race.4level)
class(comb2_sub$sex_at_birth)
```

# Explore the Data

I am not a stats person, but I am assuming that your data meets the following requirements which are required for this method (from the tutorials):

1.  That you have a linear model
2.  Expected value of the residuals is equal to zero (expected value given x is equal to zero)
3.  You have constant variance (variance of the residuals given the predictors is the same regardless of what the predictors are
4.  Covariance is equal to zero

## Look at Distribution of Variables of Interest

```{r}
comb2 %>% 
  ggplot(mapping = aes(tfmri_sst_all_beh_correct.stop_rate)) +
  geom_histogram()
```

# Run the models (my data) using Leah script

```{r}
ROI_SST<-c("tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.Pre.SMA.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.Pre.SMA.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_vlPFC.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_vlPFC.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.front.gyrus.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.front.inf.front.gyrus.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_putamen.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_putamen.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_caudate.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_subcort.aseg_caudate.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_caudalanteriorcingulate.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_caudalanteriorcingulate.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_lateraloccipital.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_lateraloccipital.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsorbitalis.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_parsorbitalis.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_inferiorparietal.rh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.desikan_inferiorparietal.lh","tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.pariet.inf.supramar.rh", "tfmri_sst_all_correct.stop.vs.correct.go_beta_cort.destrieux_g.pariet.inf.supramar.lh")
#Attempt 1 for loop, Goal: Loop through each ROI to obtain beta, set, t- and p-values
SST_Disc_RESULTS<-matrix(nrow=20,ncol=4,NA)
row.names(SST_Disc_RESULTS)<-ROI_SST
for (p in 1:length(ROI_SST)){
  pp=ROI_SST[p]
  SST_DISC_MODEL<-lme(scale(comb2_sub[[pp]])~scale(Z_Score)+as.factor(race.4level)+scale(age)+as.factor(sex_at_birth),random=~1|abcd_site/rel_family_id,data=comb2_sub)
  SST_DISC_SUM<-summary(SST_DISC_MODEL)
  SST_Disc_RESULTS[p,]<-SST_DISC_SUM$coefficients[2,]
  
  
}
colnames(SST_Disc_RESULTS)<-c("beta","se","t-value","p-value")
```


