---
title: ""
author: "Doug Joubert"
date: "`r Sys.Date()`"
format: docx
editor: visual
echo: fenced
toc: true
toc-location: right
csl: ../../lsc563-joubert/apa.csl
bibliography: ../../lsc563-joubert/references.bib
---

# Introduction

## Description

## Learning Objectives

Upon completion of this class, students should be able to:

-   

## Assumptions for This Class

This class makes a few assumptions about your understanding of R and RStudio. Specifically, you have:

1.  Installed [R](https://cran.r-project.org/) and [RStudio](https://www.rstudio.com/products/RStudio/#Desktop)

2.  Experience with R and RStudio. If not, here are some resources for getting started:

    a.  [Introduction to R and RStudio](https://carpentries-incubator.github.io/R-ecology-lesson-alternative/introduction-r-rstudio.html)

    b.  [A Few Notes to Get Started with R](https://rcompanion.org/rcompanion/a_06.html)

    c.  [Getting started with R and RStudio](http://rafalab.dfci.harvard.edu/dsbook/getting-started.html)

3.  Experience creating scripts and/or markdown files

## Supplemental information contained in handout

-   

# Installing and Loading Packages

## PackageName

### Package Description (From Packages QMD)

```{r}
# install.packages("")
```

# Data Files

## About the Data

## Download the Data

The first this we need to do is download the data into our data-raw folder:

```{r}
# Download the data
```

## Load the Data

```{r}
# Use the tidyverse to read in the data
```

# References
