---
title: ""
author: "Doug Joubert"
date: "`r Sys.Date()`"
format: html
editor: visual
echo: fenced
toc: true
toc-location: right
csl: ../lsc563-joubert/apa.csl
bibliography: ../lsc563-joubert/references.bib
---

# Introduction

## Description

## Learning Objectives

Upon completion of this class, students should be able to:

-   

## Assumptions for This Class

This class makes a few assumptions about your understanding of R and RStudio.

-   

-   

## Supplemental information contained in handout

-   

# Configuration

## Installing and Loading Packages

### PackageName

```{r}
# install.packages("")
library()
```

### Tidyverse Package

The tidyverse is a collection of R [packages](https://www.tidyverse.org/packages) designed for data science. All packages share an underlying design philosophy, grammar, and data structures. Most importantly, the tidyverse collection of packages contains [ggplot](https://ggplot2.tidyverse.org/).

```{r}
# install.packages("tidyverse")
library(tidyverse)
```

# Data Files

## About the Data

## Download the Data

The first this we need to do is download the data into our data-raw folder:

```{r}
# download.file(url = "https://raw.githubusercontent.com/doujouDC/nihl-intro-r-classes/main/nihl-intro-r-classes-data-raw/blue_jays.csv",
#               destfile = "../lsc-563-joubert/data-raw/blue_jay.csv")
```

## Load the Data

# References
